### 2018-10-21 Sections/acknowledgements.tex
Touch ups

\begin{itemize}
\item We acknowledge Gavin Brennen, Joseph Clark, Eric Cavalcanti, Charlotte Bridault, Marco Tomamichel, Jonathan Olson, Samuel Marks \& Darryl Veitch \comment{Remove, since author} for helpful discussions.
\item We thank the authors of QCircuit (\href{http://physics.unm.edu/CQuIC/Qcircuit/}{http://physics.unm.edu/CQuIC/Qcircuit/}) for providing this very helpful package.
\item P.P.R is funded by an ARC Future Fellowship (project FT160100397).
\item T.B is supported by the Shanghai Research Challenge Fund; New York University Global Seed Grants for Collaborative Research; National Natural Science Foundation of China (Grant No. 61571301); the Thousand Talents Program for Distinguished Young Scholars (Grant No. D1210036A); and the NSFC Research Fund for International Young Scientists (Grant No. 11650110425); NYU-ECNU Institute of Physics at NYU Shanghai; and the Science \& Technology Commission of Shanghai Municipality (Grant No. 17ZR1443600).
\item J.P.D would like to acknowledge support from the US Air Force Office of Scientific Research, the Army Research Office, the National Science Foundation, and the Northrop-Grumman Corporation.
\item We thank almost unethical quantities of 1,3,7-Trimethylxanthine\index{Caffeine} for aiding in the motivation for this work.
\end{itemize}

>>>>

\begin{itemize}
\item We acknowledge Gavin Brennen, Joseph Clark, Eric Cavalcanti, Charlotte Bridault, Marco Tomamichel, Jonathan Olson, Samuel Marks \& Darryl Veitch \comment{Remove, since author} for helpful discussions.
\item We thank the authors of QCircuit (\href{http://physics.unm.edu/CQuIC/Qcircuit/}{http://physics.unm.edu/CQuIC/Qcircuit/}) for providing this very helpful package.
\item Peter P. Rohde is funded by an ARC Future Fellowship (project FT160100397).
\item Tim Byrnes is supported by the Shanghai Research Challenge Fund; New York University Global Seed Grants for Collaborative Research; National Natural Science Foundation of China (Grant No. 61571301); the Thousand Talents Program for Distinguished Young Scholars (Grant No. D1210036A); and the NSFC Research Fund for International Young Scientists (Grant No. 11650110425); NYU-ECNU Institute of Physics at NYU Shanghai; and the Science \& Technology Commission of Shanghai Municipality (Grant No. 17ZR1443600).
\item Jonathan P. Dowling would like to acknowledge support from the US Air Force Office of Scientific Research, the Army Research Office, the National Science Foundation, and the Northrop-Grumman Corporation.
\item We thank almost unethical quantities of 1,3,7-Trimethylxanthine\index{Caffeine} for aiding in the motivation for this work.
\end{itemize}

### 2018-10-21 Sections/essay_security_implications_of_the_global_quantum_internet.tex
Touch ups

Combined with encrypted quantum computing protocols\index{Encrypted quantum computation}, no one would even know what they were up to when using this awesome computing power, and what they learn, they could keep to themselves.
\if 1\pubmode
\else
Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}.

>>>>

Combined with encrypted quantum computing protocols\index{Encrypted quantum computation}, no one would even know what they were up to when using this awesome computing power, and what they learn, they could keep to themselves.
\if 1\pubmode
\else
Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}\footnote{\textit{``I don't even know why any of us are here. This is the worst job I've ever had."}}.

### 2018-10-21 Sections/statement_of_contributions.tex
nisq
Touch ups

\begin{itemize}
\item Peter P. Rohde conceived, directed and edited this project, developed the original ideas, and prepared most of the manuscript.
\item Zixin Huang wrote Secs.~\ref{sec:telescopy}, \ref{sec:CV_QC}, \ref{sec:essay_future_QKD}.
\item Zuen Su \& Heliang Huang prepared Part~\ref{part:SotA}.
\item William J. Munro prepared Sec.~\ref{sec:rep_net}. 
%\item Ryan L. Mann contributed to Sec.~\ref{sec:protocols_quant_int}.
\item Scott Harrison wrote Secs.~\ref{sec:econ_prop}, \ref{sec:policy} \& \ref{sec:game_theory}.
\item Tim Byrnes \& Jonathan P. Dowling wrote Sec.~\ref{sec:quant_space_race}.
\item Nana Liu \& Chris Ferrie wrote Sec.~\ref{sec:quantum_mind}.
\item Nana Liu wrote Sec.~\ref{sec:verification}.
\item All authors played active roles in the discussions that developed this work. 
\end{itemize}

\comment{Add everyone else}
\comment{Put in same order as authorship}

>>>>

\begin{itemize}
\item Peter P. Rohde conceived, directed and edited this project, developed the original ideas, and prepared most of the manuscript.
\item Zixin Huang wrote Secs.~\ref{sec:telescopy}, \ref{sec:CV_QC}, \ref{sec:essay_future_QKD} \& \ref{sec:NISQ}.
\item Heliang Huang \& Zuen Su prepared Part~\ref{part:SotA}.
\item Chris Ferrie \& Nana Liu prepared Sec.~\ref{sec:quantum_mind}.
\item Simon Devitt prepared Secs.~\ref{???}.
\item Rohit Ramakrishnan prepared Sec.~\ref{???}.
\item Si-Hui Tan \& Atul ??? contributed to Sec.~\ref{???}.
\item Nana Liu wrote Sec.~\ref{sec:verification}.
\item Scott Harrison wrote Secs.~\ref{sec:econ_prop}, \ref{sec:policy} \& \ref{sec:game_theory}.
\item Darryl Vietch contributed to Sec.~\ref{???}.
\item Chandra Radamankrishnan contributed to Sec.~\ref{???}.
\item Jonathan P. Dowling contributed to editing.
\item Tim Byrnes \& Jonathan P. Dowling wrote Sec.~\ref{sec:quant_space_race}.
\item William J. Munro prepared Sec.~\ref{sec:rep_net}. 
\item All authors played active roles in the discussions that developed this work. 
\end{itemize}
